Naturalness in U(1) extensions of the MSSM

### 2014-12-17 paper/e6ssm-tuning-paper.tex
Added in possible paragraph for describing why fine tuning depends on charges

The exact level of tuning from the $Z^\prime$ depends on the charges of
the extra $U(1)$ gauge symmetry it is associated with.  In Fig \ref{}
we look at the fine tuning for other U(1) extensions for the same
$Z^\prime$ masses as we did for the E$_6$SSM.
 % - if room, plots for different U(1)' charge Here we see that the As
can be seen in Fig.~\ref{} the severity of the tunings varies quite a
bit.  This is because the charges appear as coefficients in front of
the $Z^\prime$ mass in the EWSB condition.  These cagres change the
value of the coefficient $d$ in Eq.~\ref{}.  The values of the
coefficient $d$ in each model is [insert], and this determines which
of the models are most tuned.

>>>>

The exact level of tuning from the $Z^\prime$ depends on the charges of
the extra $U(1)$ gauge symmetry it is associated with.  In Fig \ref{}
we look at the fine tuning for other U(1) extensions for the same
$Z^\prime$ masses as we did for the E$_6$SSM.
% - plots for different U(1)' charge 
% DH:: not quite sure of the standard way of setting up subfigures...

As can be seen in Fig.~\ref{} the severity of the tunings varies quite a
bit.  This is because the charges appear as coefficients in front of
the $Z^\prime$ mass in the EWSB condition.  These cagres change the
value of the coefficient $d$ in Eq.~\ref{}.  The values of the
coefficient $d$ in each model is [insert], and this determines which
of the models are most tuned.\\ \\

% DH:: I didn't use the d notation in the section on EWSB, would this
% work to introduce it here instead?
While the $Z^\prime$ mass does set a lower limit on the tuning, the exact
value of this tuning depends quite strongly on the charges of the extra
$U(1)$ gauge symmetry it is associated with. This is illustrated in Fig~\ref{}, 
in which we show the fine tuning for several other commonly studied
$U(1)$ extensions for the same set of $Z^\prime$ masses as were considered in the
E$_6$SSM. As can be seen in Fig.~\ref{}, the severity of the tunings varies
quite a bit. This can be understood from the fact that the $D$-terms $D_{H_d}$, $D_{H_u}$
that enter the EWSB condition Eq. (\ref{eq:E6MZequation}) are proportional to
the $U(1)'$ charges. It is therefore possible to significantly reduce the size
of the additional $D$-term contributions to the EWSB conditions by choosing the $U(1)'$ 
charges appropriately. For $s\gg v$, as is
required in all of the $U(1)$ extended models considered in order to have $M_{Z^\prime}\geq 2.5$ TeV,
the $D$-term contribution to Eq. (\ref{eq:E6MZequation}) is well approximated by
\begin{equation*}
\frac{D_{H_d}-D_{H_u}\tan^2\beta}{\tan^2-1}\approx \frac{g_1'^2}{2}\tilde{Q}_Ss^2\left ( \frac{\tilde{Q}_1-\tilde{Q}_2\tan^2\beta}{\tan^2\beta-1}\right )\approx d(\theta,\tan\beta)\frac{M_{Z^\prime}^2}{2},\qquad d(\theta,\tan\beta)\equiv \left ( \frac{\tilde{Q}_1-\tilde{Q}_2\tan^2\beta}{\tilde{Q}_S\left ( \tan^2\beta - 1\right )}\right ) 
\end{equation*}
for models with $\tilde{Q}_S\neq 0$. Written in this form one might expect that the fine tuning
associated with this contribution will be reduced when this expression is 
minimised. This is indeed the case. For example, in the E$_6$SSM with $\theta=\arctan\sqrt{15}$ one finds that for $\tan\beta=10$, $d\approx 0.398$. This can be compared to the $U(1)_\psi$ ($\theta=\pi/2$) and $U(1)_\eta$ ($\theta=-\arctan\sqrt{5/3}$) models, for which $d=0.5$ and $d\approx 0.806$, respectively. The larger values of the $D$-term contributions in these models result in them having a larger fine tuning than in the E$_6$SSM, as is evident from Fig.~\ref{}. Of particular note is the inert $U(1)_I$ model ($\theta=\pi+\arctan\sqrt{3/5}$), which has $\tilde{Q}_2=0$, resulting in the coefficient $d$ being suppressed by $\tan^2\beta$. For this model we find that $d\approx-0.01$, and so the $D$-term contribution is much smaller than in the other models described. The fine tuning is as a result somewhat smaller, not being much greater than that found in the MSSM.
